Bandit Multiclass Classification

### 2018-10-12 ptf_margin.tex
margin lower bounds (proof not written yet)

\section{Learning intersection of halfspaces with a margin}
Suppose we are given examples $S = \cbr{(x, y)}$, where $x$ is in $\cbr{x \in \fR^d: \| x \| \leq 1}$, and $y$ is in $\cbr{-1,+1}$.
\begin{definition}
$S$ is said to be separable by an intersection of halfspaces with margin parameter $\gamma > 0$, if there exists $t$ linear classifiers $v_1, \ldots, v_t$ (all of which are in $\cbr{v \in \fR^d: \| v \| \leq 1}$),
such that for every $(x,y)$ in $S$:
\begin{enumerate}
  \item If $y = +1$, then $v_i \cdot x \geq \gamma$ holds simultaneously for all $i$ in $[t]$.
  \item If $y = -1$, then there exists an $i$ in $[t]$, $v_i \cdot x \leq -\gamma$.
\end{enumerate}
\label{def:int-margin}
\end{definition}

Given a set $S$ separable by an intersection of halfspaces with a margin $\gamma$, our goal is to find a feature map $\phi: \fR^d \to \fR^{d'}$, such that the dataset $S' = \cbr{(\phi(x), y): (x,y) \in S}$ is linearly separable by a margin $\gamma' > 0$. That is, for every $(\phi(x), y)$ in $S'$, and
there exists a vector $u$ in $\fR^{d'}$, such that for every $(\phi(x), y)$ in $S'$, $\frac{y u \cdot \phi(x)}{\|u\|\| \phi(x)\|} \geq \gamma'$.
In addition, we would like our feature map $\phi$ to correspond to a kernel function $k(x,x') = \inner{\phi(x), \phi(x')}$ that can be efficiently evaluated.

\section{Construction of polynomials}
Our $\phi$'s in considerations are as follows: TODO: fix the constant in phi so that it has norm at most 1.
\begin{enumerate}
\item $\phi_1(x) = (x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0} = (x_S)_{S \in N^d, \|S\|_1 \leq \deg}$. This corresponds to the complete symmetric kernel $K_{\deg}$.
\item $\phi_2(x) = ( \sqrt{ {\deg \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$. This corresponds to the polynomial kernel
$K_{\deg}'(x,x') = (1 + \inner{x, x'})^{\deg}$.
\item $\phi_3(x) = ( \sqrt{ (\frac 1 2)^{i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq \deg, i_1, \ldots, i_d \geq 0}$. This corresponds to the kernel $K(x,x') = \frac{1}{1 - \frac 1 2 \inner{x,x'}}$.
\end{enumerate}

For a polynomial $p = \sum_{S \in \fN^d} c_S x_S$, define $\|p\|$, the norm of $p$, as the $\ell_2$ norm of the vector that contains its coefficients on every monomial, that is $\|p\| = \| (c_S)_{S \in \fN^d} \| = \sqrt{\sum_{S \in \fN^d} c_S^2}$. This is also the RKHS norm of $p$ wrt the complete symmetric kernel $K_{\deg}$, for $\deg \geq \deg(p)$.

@@

\begin{lemma}[~\cite{klivans2004learning}]
For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y Q(x) \geq \frac 1 2$.
As a consequence, $y p(x) \geq 2^{\frac{n(n-1)h(2t)t}2 - 2}$.
\end{lemma}
\begin{proof}
We consider two cases regarding the label of the example.
\begin{enumerate}
\item Suppose $y = 1$, then for all $i$ in $[t]$, $v_i \cdot x \in [\gamma, 1]$. This implies that $\frac{v_i \cdot x}{\gamma} \in [1, \frac 1 \gamma]$.
By item~\ref{item:sign-rt} of Fact~\ref{fact:newman}, we have that $D_i(x) \in [1, 1+ \frac 1 {2t}]$.
Hence, $Q(x) \geq t - (t - \frac 1 2) \geq \frac 1 2$.

\item Suppose $y = -1$. First observe that for all $i$ in $[t]$, $\frac{v_i \cdot x}{\gamma} \in [-\frac 1\gamma, \frac 1 \gamma]$. By items~\ref{item:sign-rt},
~\ref{item:sign-lt} and~\ref{item:sign-mid} of Fact~\ref{fact:newman}, we have that $S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) \leq 1+ \frac 1 {2t}$.
In addition, by Definition~\ref{def:int-margin}, there exists an $i_0$ in $[t]$, such that $v_{i_0} \cdot x \leq -\gamma$.
By item~\ref{item:bound-out} of Fact~\ref{fact:cheb}, we have that
$D_{i_0}(x) \in [-1 - \frac 1 {2t}, -1]$.
Hence,
\[ Q(x) = D_{i_0}(x) + \sum_{i \neq i_0} D_i(x) - (t - \frac 1 2)
\leq -1 + (t-1)(1 + \frac 1 {2t}) - (t - \frac 1 2) \leq - \frac 1 2. \]
%\leq -1 + t-1 + \frac{t-1}{2t} - (t - \frac 1 2)
\end{enumerate}
To summarize, we have shown that for all $(x,y)$ in $S$, $y Q(x) \geq \frac 1 2$.
Therefore,
\[ y p(x) = y Q(x) \cdot \prod_{i=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}\gamma) \geq \frac 1 2 ((1-\frac{1}{4t+1}) \cdot 2^{\frac{n(n-1)h(2t)}2})^t \geq 2^{\frac{n(n-1)h(2t)t}2 - 2}. \]
\end{proof}

\begin{fact}
$S_n^k(\cdot)$ has the following properties:
\begin{enumerate}
\item If $x$ is in $[1, 2^n]$, then $S_n^k(x)$ is in $[1, 1 + \frac 1 k]$. \label{item:sign-rt}
\item If $x$ is in $[-2^{-n}, -1]$, then $S_n^k(x)$ is in $[-1 - \frac 1 k, -1]$. \label{item:sign-lt}
\item If $x$ is in $[-1, 1]$, then $|S_n^k(x)|$ is in $[-1, 1]$. \label{item:sign-mid}
\item For all $x$ in $[-2^{-n}, 2^{-n}]$, $B_n^k(x) \geq (1-\frac{1}{2k+1}) \cdot 2^{\frac{n(n-1)h(k)}2}$. \label{item:sign-denom}
\end{enumerate}
\label{fact:newman}
\end{fact}
\begin{proof}
We prove all the items accordingly.
\begin{enumerate}
\item Observe that $S_n^k(x)$ can be written as:
\[ S_n^k(x) = \frac{1 + (-\frac{P_n(x)}{P_n(-x)})^{h(k)}}{ 1 - (-\frac{P_n(x)}{P_n(-x)})^{h(k)} }.  \]
Denote by $r = (-\frac{P_n(x)}{P_n(-x)})^{h(k)}$. By item~\ref{item:x-large} of Fact~\ref{fact:pn}, $r \in [0, \frac{1}{2k+1}]$. This implies that
$S_n^k(x) = \frac{1+r}{1-r} \in [1, 1 + \frac 1 k]$.

@@

\item Noticing that $B_n^k(x)$ is an even function, without loss of generality, suppose $x \geq 0$.
First, note that if $x \geq 0$, then $\abs{P_n(-x)} \geq \prod_{i=1}^n 2^{2i} = 2^{n(n-1)}$.
If $x$ is in $[1,2^n]$, then $B_n^k(x) = \abs{P_n(-x)^{h(k)}} (1 - r) \geq \abs{P_n(-x)^{h(k)}} \cdot \frac{2k}{2k+1} \geq 2^{n(n-1)h(k)} \cdot \frac{2k}{2k+1}$.
If $x$ is in $[0,1]$, as both $P_n(-x)$ and $-P_n(x)$ are $\leq 0$, we have $B_n^k(x) \geq \abs{P_n(-x)^{h(k)}} \geq 2^{n(n-1)h(k)}$. Therefore, for all $x \in [0,2^n]$,
$\abs{B_n^k(x)} \geq (1-\frac{1}{2k+1}) 2^{n(n-1)h(k)$.
\end{enumerate}
\end{proof}

\paragraph{Norm bound.} We bound the norm of $p$ using the theorem below.
\begin{theorem}
$p(x)$ can be written as $\inner{c, \phi_1(x)}$ for some $c$ such that $\|c\| \leq$.
\end{theorem}
\begin{proof}
Let $n = \ceil{\log \frac 1 \gamma}$.

First, for all $i$ in $[t]$ and $l$ in $\cbr{0,1,\ldots,n}$,
\[ \| (\frac{v_i \cdot x}{\gamma} - 2^l) \|^2 \leq \frac{1}{\gamma^2} + 2^{2l} \leq 2 \cdot 2^{2n}. \]
This implies that
\[ \| P_n(\frac{v_i \cdot x}{\gamma}) \|^2 \leq ((4n+2) \cdot 2^{2n})^{2n+1}. \]
Therefore,
\[ \| P_n(\frac{v_i \cdot x}{\gamma})^{h(k)} \|^2 \leq h(k)^{(2n+1)h(k)} \cdot ((4n+2) \cdot 2^{2n})^{(2n+1)h(k)}. \]
%$A_n^k(x) = P_n(x)^{h(k)} - P_n(-x)^{h(k)}$, $B_n^k(x) = -P_n(-x)^{h(k)} - P_n(x)^{h(k)}$
By the definition of $A_n^k$ and $B_n^k$, we have
\[ \| A_n^k(\frac{v_i \cdot x}{\gamma}) \|^2,  \| B_n^k(\frac{v_i \cdot x}{\gamma}) \|^2 \leq ((8n+4) h(k) \cdot 2^{2n})^{(2n+1)h(k)}. \]

%\sum_{i=1}^t A_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) \cdot \prod_{j \neq i} B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) - (t-\frac12) \prod_{j=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma})
Hence, for every $i$ in $[t]$,
\[
\| A_n^{2t}(\frac{v_i \cdot x}{\gamma}) \cdot \prod_{j \neq i} B_n^{2t}(\frac{v_j \cdot x}{\gamma}) \|^2
\leq
t^{(2n+1) h(k) t} \cdot ((8n+4) h(k) \cdot 2^{2n})^{(2n+1)h(k)t}.
\]
Similarly,
\[
\| \prod_{i=1}^t B_n^{2t}(\frac{v_i \cdot x}{\gamma}) \|^2 \leq t^{(2n+1) h(k) t} \cdot ((8n+4) h(k) \cdot 2^{2n})^{(2n+1)h(k)t}.
\]
Therefore,
\[
\| p(x) \|^2 \leq ((t - \frac 1 2)^2 + t) \cdot ((8n+4) h(k) t \cdot 2^{2n})^{(2n+1)h(k)t} \leq ((16n+8) h(k) t \cdot 2^{2n})^{(2n+1)h(k)t}.
\]
where the last inequality uses that $2^{(2n+1)h(k)t} \geq t^2 + \frac 1 4$.

@@

For the first item, given that $x \in [0,1]$, $-(-x-1) \geq 1-x \geq 0$. Therefore,
\[ \frac{-P_n(-x)}{-P_n(x)} = \frac{-(-x-1)}{1-x} \prod_{i =1}^n \frac{(x+2^i)^2}{(x - 2^i)^2}  \geq 1. \]

For the second item, given that $x \geq 1$, $-(-x-1) \geq x-1 \geq 0$. In addition, as $x$ is in $[1,2^n]$, there exists an $i_0 \in [n]$ such that $2^{i_0-1} \leq x \leq 2^i_0$. Therefore,
$(x+2^i)^2 \geq 4(x - 2^i)^2$. Hence,
\[ \frac{-P_n(-x)}{P_n(x)} = \frac{-(-x-1)}{ x-1} \prod_{i \neq i_0} \frac{(x+2^i)^2}{(x - 2^i)^2} \frac{(x+2^{i_0})^2}{(x - 2^{i_0})^2} \geq 4. \]

\subsection{Construction using Chebyshev polynomials}
\paragraph{The construction.} Define
\[ p(x) = t + \frac 1 2 - \sum_{i=1}^t (T_{\ceil{\sqrt{\frac 2 \gamma}}}(1 - v_i \cdot x))^{\ceil{\log 2t}}, \]
where
$T_r(\cdot)$ is the $r$-th order Chebyshev polynomial. Denote by $C_i(x) = (T_{\ceil{\sqrt{\frac 2 \gamma}}}(1 - v_i \cdot x))^{\ceil{\log 2t}}$. $p$ can therefore be simplified to
\[ p(x) = t + \frac 1 2 - \sum_{i=1}^t C_i(x). \]

@@

\item Suppose $y = -1$. First observe that for all $i$, $T_{\ceil{\sqrt{\frac 2 \gamma}}}(1 - v_i \cdot x)) \geq -1$. This is because of items~\ref{item:bound-in} and~\ref{item:bound-out} of Fact~\ref{fact:cheb}.
This implies that $C_i(x) \geq -1$.
On the other hand, by Definition~\ref{def:int-margin}, there exists an $i_0$ in $[t]$, such that $v_{i_0} \cdot x \leq -\gamma$. By item~\ref{item:bound-out} of Fact~\ref{fact:cheb}, we have that
$C_{i_0}(x) \geq (1 + \gamma \cdot \frac 1 \gamma)^{\ceil{\log 2t}} \geq 2t$. Therefore,
\[ p(x) = t + \frac 1 2 - C_{i_0}(x) - \sum_{i \neq i_0} C_i(x) \leq t + \frac 1 2 - 2t + (t-1) \leq -\frac 1 2. \]
\end{enumerate}
\end{proof}

>>>>

\section{Learning intersection of halfspaces with a margin}
Suppose we are given examples $S = \cbr{(x, y)}$, where $x$ is in $\cbr{x \in \fR^d: \| x \| \leq 1}$, and $y$ is in $\cbr{-1,+1}$.
\begin{definition}
Dataset $S$ is said to be separable by an intersection of halfspaces with margin parameter $\gamma > 0$, if there exists $t$ linear classifiers $v_1, \ldots, v_t$ (all of which are in $\cbr{v \in \fR^d: \| v \| \leq 1}$),
such that for every $(x,y)$ in $S$:
\begin{enumerate}
  \item If $y = +1$, then $v_i \cdot x \geq \gamma$ holds simultaneously for all $i$ in $[t]$.
  \item If $y = -1$, then there exists an $i$ in $[t]$, $v_i \cdot x \leq -\gamma$.
\end{enumerate}
\label{def:int-margin}
\end{definition}

Given a set $S$ separable by an intersection of halfspaces with a margin $\gamma$, our goal is to find a feature map $\phi: \fR^d \to \fR^{d'}$, such that the dataset $S' = \cbr{(\phi(x), y): (x,y) \in S}$ is linearly separable by a margin $\gamma' > 0$.
\begin{definition}
Dataset $T$ is said to be separable by halfspace with margin parameter $\rho > 0$, if there exists a linear classifier $u$, such that,
\[ \min_{(x,y) \in T} y u \cdot x \geq \rho \|u\| \max_{(x,y) \in T} \| x \|. \]
\end{definition}

That is,
there exists a vector $u$ in $\fR^{d'}$, such that $\min_{(x,y) \in S} y u \cdot \phi(x) \geq \gamma' \|u\| \max_{(x,y) \in S} \| \phi(x) \|$.
In addition, we would like our feature map $\phi$ to correspond to a kernel function $k(x,x') = \inner{\phi(x), \phi(x')}$ that can be efficiently evaluated.

\section{Construction of polynomials}
Our $\phi$'s in considerations are as follows:
\begin{enumerate}
%\sqrt{\frac{1}{\deg+1}}
\item $\phi_{s}(x) = ( x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq s, i_1, \ldots, i_d \geq 0} = (x_S)_{S \in N^d, \|S\|_1 \leq s}$. This corresponds to the complete symmetric kernel $K_s$. Note that for all $x$ such that $\| x \|_2 \leq 1$,
$\inner{\phi_{s}(x), \phi_{s}(x)} \leq \sum_{i=0}^s \|x\|^{2i} \leq 1 + s$.

%\frac{1}{2^{\deg}}
\item $\phi_{s}'(x) = ( \sqrt{ {s \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1 + \ldots + i_d \leq s, i_1, \ldots, i_d \geq 0}$. This corresponds to the polynomial kernel
$K_s'(x,x') = (1 + \inner{x, x'})^s$. Note that for all $x$ such that $\| x \|_2 \leq 1$,
$\inner{\phi_s'(x), \phi_s'(x)} = K_s'(x,x) = (1 + \|x\|^2)^s \leq 2^s$.

\item $\phi_0(x) = ( \sqrt{ (\frac 1 2)^{i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}  x_1^{i_1} \ldots x_d^{i_d})_{i_1, \ldots, i_d \geq 0}$. This corresponds to the kernel $K(x,x') = \frac{1}{1 - \frac 1 2 \inner{x,x'}}$.
Note that for all $x$ such that $\| x \|_2 \leq 1$,
$\inner{\phi_0(x), \phi_0(x)} = K(x,x) \leq 2$.
\end{enumerate}

For a polynomial $p = \sum_{S \in \fN^d} c_S x_S$, define $\|p\|$, the norm of $p$, as the $\ell_2$ norm of the vector that contains its coefficients on every monomial, that is $\|p\| = \| (c_S)_{S \in \fN^d} \| = \sqrt{\sum_{S \in \fN^d} c_S^2}$. We have the following simple result.
\begin{lemma}
Suppose polynomial $p$ has degree $\deg$, and has norm $\|p\|$. Then
\begin{enumerate}
\item For any degree $s \geq \deg$, $p$ can be written as $\inner{c, \phi_s(x)}$, where $\|c\| = \|p\|$.
\item For any degree $s \geq \deg$, $p$ can be written as $\inner{c', \phi_s'(x)}$, where $\|c_0\| \leq \|p\|$.
\item $p$ can be written as $\inner{c_0, \phi_0(x)}$, where $\|c_0\| \leq 2^{\frac{\deg}{2}} \|p\|$.
\end{enumerate}
\end{lemma}
\begin{proof}
Note that $p(x)$ can be written as $\sum_{i_1,\ldots,i_d \in \fN} c_{i_1,\ldots,i_d} x_1^{i_1} \ldots x_d^{i_d}$. As $p$ has degree $\deg$, $c_{i_1,\ldots,i_d} = 0$ for $i_1 + \ldots + i_d > \deg$.

The first item follows as $\phi_s(x)$ contains all monomials in $p$.

For the second item, we define $(c')_{i_1,\ldots,i_d} = \frac{c_{i_1,\ldots,i_d}}{\sqrt{ {s \choose i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}}$ for all $(i_1,\ldots,i_d) \in \fN, i_1+\ldots+i_d \leq s$. It can be seen that $\inner{c', \phi_s'(x)} = \inner{c, \phi_s(x)}$, and
$\| c' \| \leq \| c \| = \| p \|$.

For the third item, we define $(c_0)_{i_1,\ldots,i_d} = \frac{c_{i_1,\ldots,i_d}}{\sqrt{ (\frac 1 2)^{i_1+\ldots+i_d} {i_1+\ldots+i_d \choose i_1 \ldots i_d}}}$ for all $(i_1,\ldots,i_d) \in \fN$. As $c_{i_1,\ldots,i_d} = 0$ for $i_1 + \ldots + i_d > \deg$, $|(c_0)_{i_1,\ldots,i_d}| \leq 2^{\frac{\deg}{2}} |c_{i_1,\ldots,i_d}|$.
This implies that
$\| c_0 \| \leq 2^{\frac{\deg}{2}} \| c \| = 2^{\frac{\deg}{2}} \| p \| $.
\end{proof}

%This is also the RKHS norm of $p$ wrt the complete symmetric kernel $K_{\deg}$, for $\deg \geq \deg(p)$.

@@

\begin{lemma}[~\cite{klivans2004learning}]
For all $(x,y)$ in $S$ satisfying Definition~\ref{def:int-margin}, we have that $y Q(x) \geq \frac 1 2$.
As a consequence, $y p(x) \geq 2^{n(n-1)h(2t)t - 2}$.
\end{lemma}
\begin{proof}
We consider two cases regarding the label of the example.
\begin{enumerate}
\item Suppose $y = 1$, then for all $i$ in $[t]$, $v_i \cdot x \in [\gamma, 1]$. This implies that $\frac{v_i \cdot x}{\gamma} \in [1, \frac 1 \gamma]$.
By item~\ref{item:sign-rt} of Fact~\ref{fact:newman}, we have that $D_i(x) \in [1, 1+ \frac 1 {2t}]$.
Hence, $Q(x) \geq t - (t - \frac 1 2) \geq \frac 1 2$.

\item Suppose $y = -1$. First observe that for all $i$ in $[t]$, $\frac{v_i \cdot x}{\gamma} \in [-\frac 1\gamma, \frac 1 \gamma]$. By items~\ref{item:sign-rt},
~\ref{item:sign-lt} and~\ref{item:sign-mid} of Fact~\ref{fact:newman}, we have that $S_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) \leq 1+ \frac 1 {2t}$.
In addition, by Definition~\ref{def:int-margin}, there exists an $i_0$ in $[t]$, such that $v_{i_0} \cdot x \leq -\gamma$.
By item~\ref{item:bound-out} of Fact~\ref{fact:cheb}, we have that
$D_{i_0}(x) \in [-1 - \frac 1 {2t}, -1]$.
Hence,
\[ Q(x) = D_{i_0}(x) + \sum_{i \neq i_0} D_i(x) - (t - \frac 1 2)
\leq -1 + (t-1)(1 + \frac 1 {2t}) - (t - \frac 1 2) \leq - \frac 1 2. \]
%\leq -1 + t-1 + \frac{t-1}{2t} - (t - \frac 1 2)
\end{enumerate}
To summarize, we have shown that for all $(x,y)$ in $S$, $y Q(x) \geq \frac 1 2$.
Therefore,
\[ y p(x) = y Q(x) \cdot \prod_{i=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}\gamma) \geq \frac 1 2 ((1-\frac{1}{4t+1}) \cdot 2^{n(n-1)h(2t)})^t \geq 2^{n(n-1)h(2t)t - 2}. \]
\end{proof}

\begin{fact}
$S_n^k(\cdot)$ has the following properties:
\begin{enumerate}
\item If $x$ is in $[1, 2^n]$, then $S_n^k(x)$ is in $[1, 1 + \frac 1 k]$. \label{item:sign-rt}
\item If $x$ is in $[-2^{-n}, -1]$, then $S_n^k(x)$ is in $[-1 - \frac 1 k, -1]$. \label{item:sign-lt}
\item If $x$ is in $[-1, 1]$, then $|S_n^k(x)|$ is in $[-1, 1]$. \label{item:sign-mid}
\item For all $x$ in $[-2^{-n}, 2^{-n}]$, $B_n^k(x) \geq (1-\frac{1}{2k+1}) \cdot 2^{n(n-1)h(k)}$. \label{item:sign-denom}
\end{enumerate}
\label{fact:newman}
\end{fact}
\begin{proof}
We prove all the items accordingly.
\begin{enumerate}
\item Observe that $S_n^k(x)$ can be written as:
\[ S_n^k(x) = \frac{1 + (-\frac{P_n(x)}{P_n(-x)})^{h(k)}}{ 1 - (-\frac{P_n(x)}{P_n(-x)})^{h(k)} }.  \]
Denote by $r = (-\frac{P_n(x)}{P_n(-x)})^{h(k)}$. By item~\ref{item:x-large} of Fact~\ref{fact:pn}, $r \in [0, \frac{1}{2k+1}]$. This implies that
$S_n^k(x) = \frac{1+r}{1-r} \in [1, 1 + \frac 1 k]$.

@@

\item Noticing that $B_n^k(x)$ is an even function, without loss of generality, suppose $x \geq 0$.
First, note that if $x \geq 0$, then $\abs{P_n(-x)} \geq \prod_{i=1}^n 2^{2i} = 2^{n(n-1)}$.
If $x$ is in $[1,2^n]$, then $B_n^k(x) = \abs{P_n(-x)^{h(k)}} (1 - r) \geq \abs{P_n(-x)^{h(k)}} \cdot \frac{2k}{2k+1} \geq 2^{n(n-1)h(k)} \cdot \frac{2k}{2k+1}$.
If $x$ is in $[0,1]$, as both $P_n(-x)$ and $-P_n(x)$ are $\leq 0$, we have $B_n^k(x) \geq \abs{P_n(-x)^{h(k)}} \geq 2^{n(n-1)h(k)}$. Therefore, for all $x \in [0,2^n]$,
$\abs{B_n^k(x)} \geq (1-\frac{1}{2k+1}) 2^{n(n-1)h(k)}$.
\end{enumerate}
\end{proof}

\paragraph{Norm bound.} We bound the norm of $p$ in the theorem below.
\begin{theorem}
$p(x)$ has degree $\deg = (2\ceil{\log \frac 1 \gamma}+1)h(2t)t$, and has norm $\|p\| \leq ((16\ceil{\log \frac 1 \gamma}+8) h(2t) t \cdot \frac 1 \gamma)^{(2\ceil{\log \frac 1 \gamma}+1)h(2t)t}$.
\end{theorem}
\begin{proof}
The degree of $p$ follows from the
Let $n = \ceil{\log \frac 1 \gamma}$.

First, for all $i$ in $[t]$ and $l$ in $\cbr{0,1,\ldots,n}$,
\[ \| (\frac{v_i \cdot x}{\gamma} - 2^l) \|^2 \leq \frac{1}{\gamma^2} + 2^{2l} \leq 2 \cdot 2^{2n}. \]
This implies that
\[ \| P_n(\frac{v_i \cdot x}{\gamma}) \|^2 \leq ((4n+2) \cdot 2^{2n})^{2n+1}. \]
Therefore,
\[ \| P_n(\frac{v_i \cdot x}{\gamma})^{h(2t)} \|^2 \leq h(2t)^{(2n+1)h(2t)} \cdot ((4n+2) \cdot 2^{2n})^{(2n+1)h(2t)}. \]
%$A_n^k(x) = P_n(x)^{h(k)} - P_n(-x)^{h(k)}$, $B_n^k(x) = -P_n(-x)^{h(k)} - P_n(x)^{h(k)}$
By the definition of $A_n^k$ and $B_n^k$, we have
\[ \| A_n^{2t}(\frac{v_i \cdot x}{\gamma}) \|^2,  \| B_n^{2t}(\frac{v_i \cdot x}{\gamma}) \|^2 \leq ((8n+4) h(2t) \cdot 2^{2n})^{(2n+1)h(2t)}. \]

%\sum_{i=1}^t A_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) \cdot \prod_{j \neq i} B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma}) - (t-\frac12) \prod_{j=1}^t B_{\ceil{\log \frac 1 \gamma}}^{2t}(\frac{v_i \cdot x}{\gamma})
Hence, for every $i$ in $[t]$,
\[
\| A_n^{2t}(\frac{v_i \cdot x}{\gamma}) \cdot \prod_{j \neq i} B_n^{2t}(\frac{v_j \cdot x}{\gamma}) \|^2
\leq
t^{(2n+1) h(2t) t} \cdot ((8n+4) h(2t) \cdot 2^{2n})^{(2n+1)h(2t)t}.
\]
Similarly,
\[
\| \prod_{i=1}^t B_n^{2t}(\frac{v_i \cdot x}{\gamma}) \|^2 \leq t^{(2n+1) h(2t) t} \cdot ((8n+4) h(2t) \cdot 2^{2n})^{(2n+1)h(2t)t}.
\]
Therefore,
\[
\| p(x) \|^2 \leq ((t - \frac 1 2)^2 + t) \cdot ((8n+4) h(2t) t \cdot 2^{2n})^{(2n+1)h(2t)t} \leq ((16n+8) h(2t) t \cdot 2^{2n})^{(2n+1)h(2t)t}.
\]
where the second inequality uses that $2^{(2n+1)h(2t)t} \geq t^2 + \frac 1 4$.
This implies that $p(x)$ can be written as $\inner{c, \phi_1(x)}$, where $\| c \|_2^2 \leq ((16n+8) h(2t) t \cdot 2^{2n})^{(2n+1)h(2t)t}$. Taking square roots on both sides, the theorem follows from algebra.
%Hence, $\| c \|_2 \leq ((16n+8) h(2t) t \cdot 2^n)^{(2n+1)h(2t)t}$.
\end{proof}

For the first item, given that $x \in [0,1]$, $1+x \geq 1-x \geq 0$. Therefore,
\[ \frac{-P_n(-x)}{-P_n(x)} = \frac{1+x}{1-x} \prod_{i =1}^n \frac{(x+2^i)^2}{(x - 2^i)^2}  \geq 1. \]

For the second item, given that $x \geq 1$, $1+x \geq x-1 \geq 0$. In addition, as $x$ is in $[1,2^n]$, there exists an $i_0 \in [n]$ such that $2^{i_0-1} \leq x \leq 2^i_0$. Therefore,
$(x+2^i)^2 \geq 4(x - 2^i)^2$. Hence,
\[ \frac{-P_n(-x)}{P_n(x)} = \frac{1+x}{ x-1} \prod_{i \neq i_0} \frac{(x+2^i)^2}{(x - 2^i)^2} \frac{(x+2^{i_0})^2}{(x - 2^{i_0})^2} \geq 4. \]

@@

\subsection{Construction using Chebyshev polynomials}
\paragraph{The construction.} Define
\[ p(x) = t + \frac 1 2 - \sum_{i=1}^t (T_{\ceil{\sqrt{\frac 1 \gamma}}}(1 - v_i \cdot x))^{\ceil{\log 2t}}, \]
where
$T_r(\cdot)$ is the $r$-th order Chebyshev polynomial. Denote by $C_i(x) = (T_{\ceil{\sqrt{\frac 1 \gamma}}}(1 - v_i \cdot x))^{\ceil{\log 2t}}$. $p$ can therefore be simplified to
\[ p(x) = t + \frac 1 2 - \sum_{i=1}^t C_i(x). \]

@@

\item Suppose $y = -1$. First observe that for all $i$, $T_{\ceil{\sqrt{\frac 1 \gamma}}}(1 - v_i \cdot x)) \geq -1$. This is because of items~\ref{item:bound-in} and~\ref{item:bound-out} of Fact~\ref{fact:cheb}.
This implies that $C_i(x) \geq -1$.
On the other hand, by Definition~\ref{def:int-margin}, there exists an $i_0$ in $[t]$, such that $v_{i_0} \cdot x \leq -\gamma$. By item~\ref{item:bound-out} of Fact~\ref{fact:cheb}, we have that
$C_{i_0}(x) \geq (1 + \gamma \cdot \frac 1 \gamma)^{\ceil{\log 2t}} \geq 2t$. Therefore,
\[ p(x) = t + \frac 1 2 - C_{i_0}(x) - \sum_{i \neq i_0} C_i(x) \leq t + \frac 1 2 - 2t + (t-1) \leq -\frac 1 2. \]
\end{enumerate}
\end{proof}
